Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-01-24 supplement.tex
Add all figures

pirouette_example_20

@@

pirouette_example_21

@@

pirouette_example_17

@@

pirouette_example_22

@@

pirouette_example_26

@@

pirouette_example_23

@@

pirouette_example_3 vs pirouette_example_18

@@

pirouette_example_24

>>>>

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_20}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/example_20_314/errors.png}
  \caption{10 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/example_20_315/errors.png}
  \caption{20 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/example_20_316/errors.png}
  \caption{30 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/example_20_317/errors.png}
  \caption{40 taxa}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_21}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/example_21_314/errors.png}
  \caption{100 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/example_21_315/errors.png}
  \caption{248 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/example_21_316/errors.png}
  \caption{500 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/example_21_317/errors.png}
  \caption{1000 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/example_21_318/errors.png}
  \caption{2000 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/example_21_319/errors.png}
  \caption{4000 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/example_21_320/errors.png}
  \caption{8000 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/example_21_321/errors.png}
  \caption{16000 nucleotides}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_17}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_17/example_17_314/errors.png}
  \caption{An unliked node substitution model}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_22}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_22/example_22_314/errors.png}
  \caption{Assuming a Yule tree prior on a Yule tree}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_26}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_26/example_26_314/errors.png}
  \caption{Assuming a Yule tree prior on a BD tree}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_23}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/example_23_314/errors.png}
  \caption{Lowest likelihood}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/example_23_315/errors.png}
  \caption{Between lowest and median likelihood}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/example_23_316/errors.png}
  \caption{Median likelihood}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/example_23_317/errors.png}
  \caption{Between median and highest likelihood}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/example_23_318/errors.png}
  \caption{Highest likelihood}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_3/example_3_314/errors.png}
  \caption{Equal number of mutations}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_18/example_18_314/errors.png}
  \caption{Equal mutation rate}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_24}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24_314/errors.png}
  \caption{Per-nucleotide mutation rate of 0.0125}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24_315/errors.png}
  \caption{Per-nucleotide mutation rate of 0.025}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24_316/errors.png}
  \caption{Per-nucleotide mutation rate of 0.05}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24_317/errors.png}
  \caption{Per-nucleotide mutation rate of 0.1}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24_318/errors.png}
  \caption{Per-nucleotide mutation rate of 0.2}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24_319/errors.png}
  \caption{Per-nucleotide mutation rate of 0.4}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24_320/errors.png}
  \caption{Per-nucleotide mutation rate of 0.8}
\end{figure}
